---
title: "Documentation for the Market Snapshot Web Application"
author: "Colin Murphy"
date: "11/8/2021"
output: 
  ioslides_presentation:
    smaller: true
          
---
```{r, echo=FALSE}
suppressPackageStartupMessages(library(data.table))
suppressPackageStartupMessages(library(forecast))
suppressPackageStartupMessages(library(ggplot2))
sp <- fread('https://fred.stlouisfed.org/graph/fredgraph.csv?bgcolor=%23e1e9f0&chart_type=line&drp=0&fo=open%20sans&graph_bgcolor=%23ffffff&height=450&mode=fred&recession_bars=on&txtcolor=%23444444&ts=12&tts=12&width=1168&nt=0&thu=0&trc=0&show_legend=yes&show_axis_titles=yes&show_tooltip=yes&id=SP500&scale=left&cosd=2016-11-04&coed=2021-11-04&line_color=%234572a7&link_values=false&line_style=solid&mark_type=none&mw=3&lw=2&ost=-99999&oet=99999&mma=0&fml=a&fq=Daily%2C%20Close&fam=avg&fgst=lin&fgsnd=2020-02-01&line_index=1&transformation=lin&vintage_date=2021-11-05&revision_date=2021-11-05&nd=2011-11-07')
```

## Overview

- The goal of the web application is to provide an overview of the US equity and bond market during a user defined time period.
- There are thee main components to the application:
  - The date range input located on the left side panel
  - The *Compare Indicators* tab that contians a plot showing each market indicator's price over a given time frame
  - The *Price Prediction* tab that allows the user to select an indicator for price prediction
- Indicator price data from the FRED website.
  - [S&P 500](https://fred.stlouisfed.org/series/SP500)
  - [ICE BofA US Corporate Index Total Return Index Value ](https://fred.stlouisfed.org/series/BAMLCC0A0CMTRIV)
  - [NASDAQ Composite Index](https://fred.stlouisfed.org/series/NASDAQCOM)
    

## Data Management

Due to US Stock Exchange holidays, the FRED data has a few observations for which the price is recorded as `.`

This is dealt with by imputing the missing price data with the previous day's price. The code for this is shown below using the S&P 500 data and the `data.table` package. Once the price variable is imputed, we can make it numeric.

```{r}
sp1 <- sp[, imputed_price := fifelse(SP500 == '.', shift(SP500), SP500)]
sp[, imputed_price := as.numeric(imputed_price)]
sp[DATE %like% '12-24' | DATE %like% '12-25']
```

---

- The *Compare Indicators* tab also generates a table displaying the average price of each selected market indicator over the time period defined by the user. The general flow of the server code is as follows:  
- Define a new, empty data table
- Iterate through the three indicators
  - If the indicator is selected, subset the indicator data according the date range chosen
  - Append indicator subset the data table defined in the first step
- With the data subsetted and combined appropriatly, use data table's `by` argument to calculate the mean of each indicator's price over the desired time period.
  
## Predictions

Similarly, the *Price Prediction* tab subsets the of the selected indicator using the date range defined by the user. Then, the plot and time series prediction is generated using the `forecast` package. This process is shown below:
```{r, fig.dim=c(7,3)}
subset <- sp[DATE %between% c('2021-01-01', '2021-07-01')] 
subset$imputed_price %>%
  ts() %>%
  auto.arima() %>%
  forecast() %>%
  autoplot() + xlab('S&P 500') + ylab('Price')
```
