---
title: "Random Locations in Sacramento, CA"
author: "Colin Murphy"
date: "11/4/2021"
output: html_document
---

```{r setup, echo=FALSE}
library(leaflet)
library(data.table)

```

Sacramento is the capital of California. Lets pin some random locations around it. 
First, we store Sacramento's coordinates, then generate a data table with two columns, 
each containing 100 random uniform numbers between -.05 and .05. Next, we simply add the Sacramento 
latitude and longitude to each column respectively. Now we have a data table of 
coordinates within .05 latitudinal and longitudinal points of Sacramento. 

```{r}
sacramento <- data.table('lat' = 38.581667,'long' = -121.494444)
pts <- data.table('lat' = runif(100, min = -.05, max = .05),
                  'long' = runif(100, min = -.05, max = .05))
pts[, c('lat', 'long') := .(lat + sacramento$lat, long + sacramento$long)]
```

Finally, we can use leaflet to make a map!

```{r}
pts %>% leaflet() %>% 
  addTiles() %>% 
  addMarkers(clusterOptions = markerClusterOptions())
```

